---
output:
  pdf_document: default
  html_document: default
---
#Load Libraries
```{r,warning=FALSE,message=FALSE}
#load libraries
library(dplyr)
library(readr)
library(DT)
library(RColorBrewer)
library(ggplot2)
library(cowplot)
library(choroplethr)
library(choroplethrZip)
library(ggmap)
library(knitr)
library(tm)
library(wordcloud)
library(shiny)
```

#Read Files
```{r,eval=FALSE}
setwd("C:/Users/He Yu/Downloads")
airbnb = read_csv(file="Datasets/calendar.csv")
airbnb16 = filter(airbnb,date=="Jan-16" | date=="Feb-16" | date=="Mar-16" | date=="Apr-16" | date=="May-16" | date=="Jun-16" | date=="Jul-16" | date=="Aug-16" | date=="Sep-16" | date=="Oct-16" | date=="Nov-16" | date=="Dec-16")
airbnb16$price=as.numeric(airbnb16$price)
#View(airbnb16)
```
#Trend of the average price variation in 2016
```{r,message=FALSE}
#monthly average price
mon_avg<-NULL
mon_avg1 = airbnb16%>%group_by(date)%>%summarise(price=mean(price, na.rm=T))
#plot the point graph with fitting line
mon_avg1[1:12,1]=c("Apr","Aug","Dec","Feb","Jan","Jul","Jun","Mar","May","Nov","Oct","Sep")
mon_avg=mon_avg1
mon_avg[1,]=mon_avg1[5,]
mon_avg[2,]=mon_avg1[4,]
mon_avg[3,]=mon_avg1[8,]
mon_avg[4,]=mon_avg1[1,]
mon_avg[5,]=mon_avg1[9,]
mon_avg[6,]=mon_avg1[7,]
mon_avg[7,]=mon_avg1[6,]
mon_avg[8,]=mon_avg1[2,]
mon_avg[9,]=mon_avg1[12,]
mon_avg[10,]=mon_avg1[11,]
mon_avg[11,]=mon_avg1[10,]
mon_avg[12,]=mon_avg1[3,]
mon_avg$date <- factor(mon_avg$date, levels=unique(mon_avg$date))
ggplot(data=mon_avg, mapping = aes(date, price,group=1)) + 
  geom_smooth(se=F, color="blue")+geom_point()+ylim(180,260)+labs(title="Trend of the average price in 2016 for Airbnb in Boston")
```
#Comparison of the Average price distribution among Oct, Feb and Jun 
```{r,warning=FALSE}
#compute the monthly average price in Oct, Feb and Jun
airbnb_Oct=filter(airbnb16,date=="Oct-16")
Avg_Oct=airbnb_Oct%>%group_by(listing_id)%>%summarise(meanp=mean(price, na.rm=T))
#do similar process for Feb
airbnb_Feb=filter(airbnb16,date=="Feb-16")
Avg_Feb=airbnb_Feb%>%group_by(listing_id)%>%summarise(meanp=mean(price, na.rm=T))
#do similar process for Jun
airbnb_Jun=filter(airbnb16,date=="Jun-16")
Avg_Jun=airbnb_Jun%>%group_by(listing_id)%>%summarise(meanp=mean(price, na.rm=T))
##plot the histogram respectively
d <- ggplot(Avg_Oct, aes(meanp, fill =..count..))
d + geom_histogram(bins = 20)+
  labs(x = "Average price of October", title = "Average price distribution in October")+
  ylim(0,400)
d <- ggplot(Avg_Feb, aes(meanp, fill =..count..))
d + geom_histogram(bins = 20)+
  labs(x = "Average price of February", title = "Average price distribution in February")+
  ylim(0,400)
d <- ggplot(Avg_Jun, aes(meanp, fill =..count..))
d + geom_histogram(bins = 20)+
  labs(x = "Average price of June", title = "Average price distribution in June")+
  ylim(0,400)
#to have all three months shown on a single boxplot and histogram
merged.avg=rbind(Avg_Feb, Avg_Jun, Avg_Oct)
merged.avg$month=c(rep("Feb", nrow(Avg_Feb)),
                   rep("Jun", nrow(Avg_Jun)),
                   rep("Oct", nrow(Avg_Oct)))
merged.avg$MeanPrice=cut(merged.avg$meanp, 8)

ggplot(data = merged.avg[!is.na(merged.avg$meanp),], 
       mapping=aes(x = month, y=meanp)) + 
  geom_boxplot()

ggplot(data = merged.avg[!is.na(merged.avg$meanp),]) + 
  geom_bar(mapping = aes(x =month, fill = MeanPrice, y = (..count..)/sum(..count..)),    
           position = "dodge")+
  labs(title = "Average Price by Months", 
       y = "Percent", 
       x = "Month")

```
##Mapping out the price distribution in Suffolk City, Boston 
```{r}
#read the original list
setwd("C:/Users/He Yu/Downloads")
siteinfo = read_csv(file="Datasets/listings.csv")
locationinfo1 = siteinfo[,c(1,49,50,61)]
locationinfo1$price=as.numeric(locationinfo1$price)
locationinfo = locationinfo1[1:3000,]
#to get the zipcode for each site based on their longitude and latitude, since I save the results for grabing loctaion information to a csv file, you don't need to run this part of loop
region<-NULL
neigborhood<-NULL
for(i in 2982:3000){
  loc<-c(locationinfo[i,3],locationinfo[i,2])
  longlan<-as.numeric(loc)
  res <- revgeocode(longlan, output="more")
  region = c(region,as.character(res$postal_code))
  neigborhood = c(neigborhood,as.character(res$neighborhood))
}
locationinfo = data.frame(locationinfo,region)
locationinfo = data.frame(locationinfo,neigborhood)
write.csv(locationinfo,"D:/R/Final Project/locationinfo.csv")#save the location information we get from Google to a csv file
#to get the mean price for each neigborhood
setwd("D:/R/Final Project")
locationinfo<-read_csv(file="locationinfo.csv")#load the location information from the csv file
Avg_loc = locationinfo%>%group_by(region)%>%summarise(value=mean(price, na.rm=T))
#map the distribution for Suffolk City whose fips code is 25025
zip_choropleth(Avg_loc,
               county_zoom=25025,
               title="Airbnb price distribution in Boston",
               legend="mean price")
```

#Relationship between the price and the condition of the sites 
```{r,message=FALSE,warning=FALSE}
setwd("C:/Users/He Yu/Downloads")
airbnbdata = read_csv(file="Datasets/listings.csv")
airbnbdata=as.data.frame(airbnbdata)
airbnbdata1=airbnbdata[,c(1,52,54,55,56,57,61)]
airbnbdata1=filter(airbnbdata1,accommodates>="1" & accommodates<"9")
airbnbdata1$price=as.numeric(airbnbdata1$price)
airbnbdata1$bedrooms=as.numeric(airbnbdata1$bedrooms)
airbnbdata1$bathrooms=as.numeric(airbnbdata1$bathrooms)
airbnbdata1$beds=as.numeric(airbnbdata1$beds)
airbnbdata1$accommodates=as.numeric(airbnbdata1$accommodates)
airbnbdata1=filter(airbnbdata1,beds>0 & beds<20)

#Mean price VS bedrooms
    grouped1 = airbnbdata1 %>% group_by(bedrooms) %>% summarise(mean_price = mean(as.numeric(price), na.rm = T))
    grouped1=na.omit(grouped1)
    Numberofbedrooms <- grouped1$bedrooms
    MeanPrice <- grouped1$mean_price
    ggplot(grouped1, aes(x =Numberofbedrooms, y = MeanPrice), colour = 'red') + geom_bar(stat = 'identity')
    
#Mean Price VS people 
    grouped2 = airbnbdata1 %>% group_by(accommodates) %>% summarise(mean_price = mean(as.numeric(price), na.rm = T))
    grouped2=na.omit(grouped2)
    Numberofpeople <- grouped2$accommodates
    MeanPrice <- grouped2$mean_price
    ggplot(grouped2, aes(x =Numberofpeople, y = MeanPrice), colour = 'red') + geom_bar(stat = 'identity')
    
 #price rate per person
    mp <- c(grouped2[,2]/grouped2[,1])
    people <- c(1:13)
    table <- data.frame(people,mp)
    plot(table)
    lines(table)
```

##Word cloud to see what do customers and the host care about the residence
```{r}
setwd("C:/Users/He Yu/Downloads")
guestsanalysis = read_csv(file="Datasets/reviews.csv")
# host's description 

hosts<- Corpus(VectorSource(airbnbdata$host_about))
  
  hosts <- tm_map(hosts, stripWhitespace)
  hosts <- tm_map(hosts, tolower)
  hosts <- tm_map(hosts, removeWords, stopwords('english'))
  hosts <- tm_map(hosts, stemDocument)
  hosts<-tm_map(hosts,removeNumbers)
  hosts<-tm_map(hosts,removePunctuation)
  hosts<-tm_map(hosts,PlainTextDocument)
  hosts<-tm_map(hosts,removeWords,c('boston','airbnb','will','can','also','just','one','much','every','city','like','enjoy','best','make','place','places','living','always','please','monday','want','take','look','things','great','now','meet','need','book','since','good','trip','beautiful','well','real','many','new','love','years','people','travel','traveling','housing'))
  
  wordcloud(hosts, scale=c(2,0.5), max.words=100, random.order=FALSE, 
            rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(10, 'Paired'))
  
#guest's review
  
guests <- Corpus(VectorSource(guestsanalysis$comments))

  guests <- tm_map(guests, stripWhitespace)
  guests <- tm_map(guests, tolower)
  guests <- tm_map(guests, removeWords, stopwords('english'))
  guests <- tm_map(guests, stemDocument)
  guests<-tm_map(guests,removeNumbers)
  guests<-tm_map(guests,removePunctuation)
  guests<-tm_map(guests,PlainTextDocument)
  guests<-tm_map(guests,removeWords, c('great','boston','nice','really','nice','two','will','even','good','lovely','can','exactly','next','one','much',
                                      'feel','little','need','needed','thank','trip','place','stay','stayed','also','visit','make','staying','wonderful','airbnb','just','perfect','made'))
  
  wordcloud(guests, scale=c(2,0.5), max.words=100, random.order=FALSE, 
            rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(10, 'Paired'))


```

#A shiny app to see the condition of the sites provided by Airbnb in Boston
```{r}
shinyApp(
#ui
shinyUI(fluidPage(
  sidebarPanel(
    selectInput("n_breaks", label = "Classify:",
                choices = c('Number of bedrooms', 'Number of beds', 'Number of bathrooms', 'Number of people accommodates'), 
                selected = 'Number of bedrooms')
  ),
  mainPanel(
    plotOutput('plot')
  )
)),

#server

shinyServer(function(input, output) {
  output$plot<-renderPlot({
    if(input$n_breaks=='Number of bedrooms') {
      a<-table(airbnbdata1$bedrooms)
      pct <- round(a/sum(a)*100, digits = 1)
      lbls1 <- pct # add percents to labels 
      lbls1 <- paste(pct,"%",sep="") # ad % to labels 
      pie(a,labels = lbls1, main = 'Number of bedrooms', col=terrain.colors(length(a)))
      legend ('topright', c('0 bedroom','1 bedroom','2 bedrooms','3 bedrooms','4 bedrooms','5 bedrooms'), cex=0.8, fill = terrain.colors(length(a)))
      #pie(sample(1:10, 20, replace=T))
    }else{pie
      if(input$n_breaks== 'Number of beds'){
        b<-table(airbnbdata1$beds)
        b=as.data.frame(b)
        ##b1<-matrix(b)
        b[6,2]=sum(b[6:10,2])
        b<-b[-c(7:10),]
        pct <- round(b$Freq/sum(b$Freq)*100, digits = 1)
        lbls2 <- pct # add percents to labels 
        lbls2 <- paste(pct,"%",sep="") # ad % to labels 
        pie(b$Freq, labels = lbls2, main = 'Number of beds', col=terrain.colors(6))
        legend ('topright',
                c('1 bed','2 beds','3 beds','4 beds','5 beds','>5 beds'), 
                cex=0.8, fill = terrain.colors(6))
      }else{
        if(input$n_breaks== 'Number of bathrooms'){
          c<-table(airbnbdata1$bathrooms)
          c=as.data.frame(c)
          c[7,2]=sum(c[7:12,2])
          c<-c[-c(8:12),]
          pct <- round(c$Freq/sum(c$Freq)*100, digits = 1)
          lbls3 <- pct # add percents to labels 
          lbls3 <- paste(pct,"%",sep="") # ad % to labels 
          pie(c$Freq,labels = lbls3, main = "Number of bathrooms", col=terrain.colors(7))
          legend('topright',
                 c('0 bathroom','0.5 bathroom','1 bathroom','1.5 bathrooms','2 bathrooms','2.5 bathrooms','>2.5 bathrooms'),
                 cex=0.8, 
                 fill = terrain.colors(7))
          
        }else{
          if(input$n_breaks== 'Number of people accommodates'){
            d<-table(airbnbdata1$accommodates)
            d=as.data.frame(d)
            d[7,2]=sum(d[7:13,2])
            d<-d[-c(8:13),]
            pct <- round(d$Freq/sum(d$Freq)*100, digits = 1)
            lbls4 <- pct # add percents to labels 
            lbls4 <- paste(pct,"%",sep="") # ad % to labels 
            pie(d$Freq, labels = lbls4, main = 'Number of people accommodates', col=terrain.colors(7)) 
            legend('topright',
                   c('1 people','2 people','3 people','4 people','5 people','6 people','>6 people'),
                   cex=0.8,
                   fill = terrain.colors(7))
        }else{
          pie(sample(1:10, 20, replace=T))
    }
  }}}
  })
})
  )
```









